DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-15 paper/core/results.tex
small paper extension

The main advantage of using neural networks is constant inference time. Once the network is trained, it takes a static execution time in inference, as it's a simple feedforward process. Table \ref{tab:exec_time} shows the execution time of the discussed schedulers at 3 different input sizes. These number are produced running on \emph{Intel i5-6600K}.

We can see that the network consumes constant time in inference with different input sizes. This is because the network is trained on the maximum input length. However, HEFT and genetic algorithms execution time increases with input size. GA time increases more rapidly than HEFT, as it's a recursive optimization method but HEFT is a greedy-based method. The performance and static execution time of the network in inference make the network very useful in the situations where static scheduling environment is provided.

>>>>

The main advantage of using neural networks is constant inference time. Once the network is trained, it takes a static execution time in inference, as it's a simple feedforward process that highly supports operation parallelism. Table \ref{tab:exec_time} shows the execution time of the discussed schedulers at 3 different input sizes. These number are produced running on \emph{Intel i5-6600K}.

We can see that the network consumes constant time in inference with different input sizes. This is because the network is trained on the maximum input length. Also, neural networks operations are highly paralleled, which gives the network a very high speedup when dealing with simple feedforward process, such as network inference. However, HEFT and genetic algorithms execution time increases with input size. GA time increases more rapidly than HEFT, as it's a recursive optimization method but HEFT is a greedy-based method. The performance and static execution time of the network in inference make the network very useful in the situations where static scheduling environment is provided.
